Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2018-12-30 papers/paper/paper.tex
Add another modeling paper to paper

\section{Model}
This dynein model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex while remaining mathematically simple. The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}. The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model. The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse. The bothbound state is meant to represent the post-powerstroke pre-ADP release state, and the onebound state represents the post pre-stroke pre-MT binding state, during which ATP is hydrolyzed and phosphate is rejected. These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the recovery stroke is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-recovery conformation should dominate when unbound from MT. We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-powerstroke state while the other head goers through the entire mechanochemical cycle, neglecting other possible cycles. Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}. In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.\\

@@

Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation}. This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency. Our minimal assumptions simplify the model and rule out overfitting. However, our model neglects many features which may be important for real dynein's walk. For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}. Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head interactions \cite{tsygankovscheme, tsygankovemsimulation}, Y and Z are also neglected. Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\

>>>>

\section{Model}
This dynein model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex while remaining mathematically simple. The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}. The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model. The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse, as has been done before \cite{zhaomodel}. The bothbound state is meant to represent the post-powerstroke pre-ADP release state, and the onebound state represents the post pre-stroke pre-MT binding state, during which ATP is hydrolyzed and phosphate is rejected. These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the recovery stroke is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-recovery conformation should dominate when unbound from MT. We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-powerstroke state while the other head goers through the entire mechanochemical cycle, neglecting other possible cycles. Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}. In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.\\

@@

Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation, zhaomodel}. This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency, and to our knowledge is the first model to combine imaging and kinetics data with Brownian dynamics to quantify the influences of drag on the dynein motor. Our minimal assumptions simplify the model and rule out overfitting. However, our model neglects many features which may be important for real dynein's walk. For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}. Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head coordination \cite{tsygankovscheme, tsygankovemsimulation}, stalk flexibility???, Y and Z are also neglected. Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\
